Model to study co-evolution of trade an culture

### 2015-03-29 article.tex
last little edit for sunday

$$ 1- \abs{\dfrac{q^i_j - n_j}{ \sqrt{\abs{(q^i_j*q^i_j)-(n_j*n_j)}}}} $$

@@

@@

If a trade is possible the two agents will exchange the agreed quantities. If the trade is not possible, the agent will continue to look at random partners for this good until either a good is found or $TradeThreshold$ agents have been tried. At this point the agent will try to trade with agents producing another good. The process goes on until all goods have been tried. This trading process is described in algorithm~\ref{algo:trade}.

@@

With such a setup it is expected that the prices will converge to a ration allowing each agent to obtain a number of resources equivalent to the needs. There the price of a good should follow the following equation :

$$ hey hey $$

If such a price is reached to score of all agents should be equal to : $$ 10*1*(ngoods-1) $$

@@

@@

\todo{add innovation and imitation}
\begin{table}[h]
	\centering
	\begin{tabular}{l|c|c}
		& Rand & Eco \\\hline
		$\mu$ &A & B \\
		$\mu +\alpha$ & C & D \\
	\end{tabular}
	\caption{Experimental Setup}
	\label{tab:exp}
\end{table}

@@

\begin{table}[H]
	\centering
	\begin{tabular}{l c c}
		& Random Transmission & Eco Transmission \\
		$\mu$ & \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeA.png}}\\Setup A}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeB.png}} \\ Setup B} \\
		$\mu + \alpha$& \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeC.png}} \\ Setup C}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeD.png}} \\ Setup D}

@@

\todo{simon you have put A and S, I guess it's C and D ?}
\todo{update explanation with new graphs}
\todo{get clear names for innovation and imitaiton mechanisms}

In the setups A and D, the score evolves randomly. In the two other setups however the score is increasing. Moreover, we observe that the XXXX innovation process used in the setups A and B leads to higher convergences. Since only the ``prestige imitation" takes the score into account it is normal that only this mechanism leads higher scores. The XXXX innovation mechanism leads to lower convergences as it select prices randomly in the complete range available.

>>>>

$$ 1- \dfrac{\abs{q^i_j - n_j}}{ \sqrt{\abs{(q^i_j)^2-(n_j)^2}}} $$

@@

\begin{itemize}
	\item Both agents have enough good in their inventory
	\item The quantitie of each good  fit the will of both agents.
\end{itemize}

@@

If a trade is possible the two agents will exchange the agreed quantities. If the trade is not possible, the agent will continue to look at random partners for this good until either a good is found or $TradeThreshold$ ($\frac{Number of agent}{2}$ agents have been tried. At this point the agent will try to trade with agents producing another good. The process goes on until all goods have been tried. This trading process is described in algorithm~\ref{algo:trade}.

@@

With such a setup it is expected that the prices will converge to a ratio allowing each agent to obtain a number of resources equivalent to the needs. Knowing that,  the best possible price of a good should follow the equation :

$$\frac{V^j_i}{V^j_g} = N_i   $$
with g the produced good of the agent j and i another good which is not the one which is produced.

If such a price is reached to score of all agents should be equal to : $$ 10\times1\times(ngoods-1) $$

@@

\simon{What do you think about puting  the bentley et al resutlts cf table~\ref{tab:Bmualpha} below}

\begin{table}
	\centering
	\begin{tabular}{l|cc}
N=250\\\hline
$\mu$&$\alpha$&(SD)\\\hline
0.004&1.50&(0.02) \\
0.008&1.52&(0.02)\\
0.016&1.55&(0.03)\\
0.032&1.59&(0.06)\\
0.064&1.78&(0.08)\\
0.128&1.99&(0.04)\\
	\end{tabular}
	\begin{tabular}{l|cc}
N=500\\\hline
$\mu$&$\alpha$&(SD)\\\hline
0.004&1.53&(0.03)
0.008&1.57&(0.01)
0.016&1.61&(0.04)
0.032&1.70&(0.05)
0.064&1.81&(0.10)
0.128&1.98&(0.02)
	\end{tabular}
	\caption{Mean \& SD from \cite{bentley_random_2004} }
	\label{tab:Bmualpha}
\end{table}

@@

\todo{add innovation and imitation}
\begin{table}[h]
	\centering
	\begin{tabular}{l|c|c}
	 Imitation  Process :& Rand & Eco \\
	 Mutation Process& & \\\hline
		$\mu$ &A & B \\
		$\mu +\alpha$ & C & D \\
	\end{tabular}
	\caption{Experimental Setup}
	\label{tab:exp}
\end{table}

@@

\begin{table}[H]
	\centering
	\begin{tabular}{l c c}
		& Random Transmission & Eco Transmission \\
		$\mu$ & \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeA.png}}\\Setup A}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeC.png}} \\ Setup B} \\
		$\mu + \alpha$& \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeB.png}} \\ Setup C}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeD.png}} \\ Setup D}

@@

\todo{simon you have put A and S, I guess it's C and D ?}
\simon{It's A and C, the setup where their is no selection. But those two graph (A and B) are not good, don't take them in account. }
\todo{update explanation with new graphs}
\todo{get clear names for innovation and imitaiton mechanisms}

In the setups A and C, the score evolves randomly. In the two other setups however the score is increasing. Moreover, we observe that the XXXX innovation process used in the setups A and B leads to higher convergences. Since only the ``prestige imitation" takes the score into account it is normal that only this mechanism leads higher scores. The XXXX innovation mechanism leads to lower convergences as it select prices randomly in the complete range available.
